SoK: Defending Against Web Application Attacks: From Research Approaches to Practical Tools

### 2014-11-15 docs/questioning.tex
minor changes

Web application defenses 
crucially have to capture the presence of an attack. This, however, does not
make a defense mechanism immediately useful. A
detection mechanism must also be reliable.
Detection accuracy is gauged with the following
metrics~\cite{TDR2013,GFDLS06,A00}.
\begin{itemize}
\item {\bf Sensitivity}: the probability that an attack will be
  caught.
\item {\bf Specificity}: the probability that a normal interaction
  will not be flagged.
\item {\bf Positive Predictive Value} ({\sc ppv}): the probability that a
  reported attack is a real attack. It is the conditional probability
  that an event is an attack if the detection mechanism flags it as
  such. 
\item {\bf Negative Predictive Value} ({\sc npv}): the probability that if
  nothing is reported, no attack has taken place. It is the conditional
  probability that an event is not an attack given that the detection
  mechanism flags it as normal.
\end{itemize}

\noindent
We will focus on sensitivity and specificity; we will come back to
\textsc{ppv} and \textsc{npv} in Section~\ref{sec:lessons-learned}.
Sensitivity and specifity are defined as follows~\cite{linn2004}.
\begin{itemize}
\item True Positive (\textsc{tp}): an attack that raises an alarm.
\item True Negative (\textsc{tn}): an event that is not an attack and that does
  not raise an alarm.
\item False Positive (\textsc{fp}): an event that although it is not an attack,
  raises an alarm.
\item False Negative (\textsc{fn}): an event that although is an attack, does
  not raise an alarm.
\end{itemize}

@@

        ({\sc TP}), True Negatives ({\sc tn}), False Positives ({\sc

@@

We categorize and analyze a large set of defenses developed to detect
and prevent
the attacks described in Sections~\ref{sec:attacks} and~\ref{sec:model}.
We perform our analysis across
the dimensions discussed in the previous section,
except from availability, which we treat
separately in Section~\ref{sec:discussion}.
Due to the immense number of published works in the area, we only consider
defenses that have been proposed in publications cited more than
20 times according to Google Scholar.
We also include some recent works that have been
presented in top security conferences, even though they have been
cited less than twenty times, so that recent research is not penalized.

@@

There are three main categories of etiological approaches used to protect web
applications against injection attacks:
\emph{Parse-Tree Validation},
\emph{Policy Enforcement}, and
\emph{Instruction Set Randomization (ISR)}.

>>>>

Web application defenses 
crucially have to capture the presence of an attack. This, however, does not
make a defense mechanism immediately useful. A
detection mechanism must also be reliable.
Detection accuracy is gauged with the following
metrics~\cite{TDR2013,GFDLS06,A00}:
\begin{itemize}
\item {\bf Sensitivity}: the probability that an attack will be
  caught.
\item {\bf Specificity}: the probability that a normal interaction
  will not be flagged.
\item {\bf Positive Predictive Value} ({\sc ppv}): the probability that a
  reported attack is a real attack. It is the conditional probability
  that an event is an attack if the detection mechanism flags it as
  such. 
\item {\bf Negative Predictive Value} ({\sc npv}): the probability that if
  nothing is reported, no attack has taken place. It is the conditional
  probability that an event is not an attack given that the detection
  mechanism flags it as normal.
\end{itemize}

\noindent
We will focus on sensitivity and specificity; we will come back to
\textsc{ppv} and \textsc{npv} in Section~\ref{sec:lessons-learned}.
Sensitivity and specifity are defined as follows~\cite{linn2004}:
\begin{itemize}
\item True Positive (\textsc{tp}): an attack that raises an alarm.
\item True Negative (\textsc{tn}): an event that is not an attack and that does
  not raise an alarm.
\item False Positive (\textsc{fp}): an event that although it is not an attack,
  raises an alarm.
\item False Negative (\textsc{fn}): an event that although is an attack, does
  not raise an alarm.
\end{itemize}

@@

        ({\sc tp}), True Negatives ({\sc tn}), False Positives ({\sc

@@

We categorize and analyze a large set of defenses developed to detect
and prevent
the attacks described in Sections~\ref{sec:attacks} and~\ref{sec:model}.
We perform our analysis across
the dimensions discussed in the previous section,
except from availability, which we treat
separately in Section~\ref{sec:discussion}.
Due to the immense number of published works in the area, we only consider
defenses that have been proposed in publications cited more than
20 times according to Google Scholar~\cite{googleScholar}.
We also include some recent works that have been
presented in top security conferences, even though they have been
cited less than twenty times, so that recent research is not penalized.

@@

There are three main categories of etiological approaches used to protect web
applications against injection attacks:
\emph{Parse-Tree Validation},
\emph{Policy Enforcement}, and
\emph{Instruction Set Randomization} ({\sc isr})}.
